% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{graphicx}
%\usepackage{subfigure}
%\usepackage{subcaption}
\usepackage{color}
%\usepackage{times}
%\captionsetup{compatibility=false}



\newcommand{\ecall}{\mathsf{C}}
\newcommand{\eresp}{\mathsf{R}}
\newcommand{\ewrite}{\mathsf{Wr}}
\newcommand{\eread}{\mathsf{Rd}}
\newcommand{\ecas}{\mathsf{CAS}}
\newcommand{\trace}{\mathit{Tr}}
\newcommand{\pair}[1]{{\langle{#1}\rangle}}
\newcommand{\set}[1]{\left\{{#1}\right\}}

\newcommand{\p}{\mathbb{P} }
\newcommand{\ft}{S_f}
\newcommand{\ct}{S_c}
\newcommand{\se}{\mathit{SE}}
\newcommand{\var}{\mathit{Var}}
\newcommand{\ce}{\mathit{CE}}
\newcommand{\dr}{\mathsf{D}}

\newtheorem{myTheo}{Theorem}
\newtheorem{myDef}{Definition}

%\newenvironment{example}[1][Example]{\begin{trivlist}
%\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\newcommand{\wri}{\mathtt{write}}
\newcommand{\rea}{\mathtt{read}}
\newcommand{\hb}{\textit{happen-before }}

\usepackage{wrapfig}
\usepackage{subfigure}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Interleaving-tree Based Localization of Linearizability Faults on the Fine-grained Level}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Yang Chen\inst{1,2} \and
Zhenya Zhang\inst{3}\thanks{The work was partially done when the author was a student at Institute of Software, Chinese Academy of Sciences} \and
Peng Wu\inst{1,2}\and
Yu Zhang\inst{1,2}}
%
\authorrunning{Y. Chen et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{{State Key Laboratory of Computer Science\\Institute of Software, Chinese Academy of Sciences}\and
University of Chinese Academy of Sciences\and
National Institute of Informatics
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Linearizability is an important correctness criterion for concurrent objects. Existing work mainly focuses on linearizability verification of coarse-grained traces with operation invocations and responses only. However, when linearizability is violated, such coarse-grained traces do not provide sufficient information for reasoning about the underlying concurrent program faults. In this paper, we propose a notion of \textit{critical data race sequence} (\textit{CDRS}), based on our fine-grained trace model, to characterize concurrent program faults that cause violation of linearizability. We then develop a labeled tree model of interleaved program executions and show how to identify \textit{CDRS}es and localize concurrent program faults automatically with a specific node-labeling mechanism. We also implemented a prototype tool, FGVT, for real-world Java concurrent programs. Experiments show that our localization technique is effective, i.e., all the \textit{CDRS}es reported by FGVT indeed reveal the root causes of linearizability faults.

\keywords{Linearizability  \and Bug localization \and Concurrency \and Testing}
\end{abstract}
%
%
%
\input{fgvt}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
 \bibliographystyle{splncs04}
 \bibliography{bare_conf}
%

\end{document}
